---
title: "Homework 1"
author: "Ananya Lahiri"
date: "2026-09-26"
output: github_document
---
# Problem 1
```{r, message = FALSE}
library(tidyverse)
data("penguins", package = "palmerpenguins")
```
In the penguins dataset, it gives us information on the type of species, island, bill length, bill depth, flipper length, body mass, sex, and year. The three types of species in the dataset are Adelie, Gentoo, and Chinstrap. The types of islands are Torgersen, Biscoe, and Dream, and the dataset includes both male and female penguins. Some of the values in the dataset are NA, showing that they are missing.

There are `r nrow(penguins)` rows and `r ncol(penguins)` columns.

The mean of flipper length is `r round(mean(pull(drop_na(penguins, flipper_length_mm), flipper_length_mm)), 2)` mm.

```{r, warning = FALSE}
# Make scatterplot
ggplot(
  penguins,
  aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
  geom_point()

# Save and export scatterplot 
ggsave("penguins_scatterplot.png")
```

# Problem 2
```{r}
# Create data frame
set.seed(1234)

p2_df =  tibble(
  rand_sample = rnorm(10), 
  log_vector = rand_sample > 0,
  char_vector = c("x", "y", "z", "a", "b", "c", "d",   "e", "f", "g"),
  factor_vector = factor(c(1, 2, 3, 1, 2, 3, 1, 2, 3, 1))
)
```

```{r}
# Mean of each variable in the data frame:

mean(pull(p2_df, rand_sample))
mean(pull(p2_df, log_vector))
mean(pull(p2_df, char_vector))
mean(pull(p2_df, factor_vector))
```
When taking the mean, it worked for the random sample and logical vector, which were -0.38 and 0.4 respectively. It did not work for the character vector and factor vector, which returned NA since they are not numeric or logical variables.

```{r, results = "hide", warning = FALSE}
# Mean after using as.numeric() on variables
as.numeric(pull(p2_df, log_vector))
as.numeric(pull(p2_df, char_vector))
as.numeric(pull(p2_df, factor_vector))

```
When using as.numeric, the logical vector was converted to zeros and ones, so its mean could be calculated. The character vector returned NA since it could not be converted to numbers, and therefore the mean was not able to be calculated. The mean was also not calculated for the factor vector since its values are categorical, even though as.numeric converted the factor levels to numbers.

